---
title: "swissrain data code"
author: "ruoyong"
date: '2022-05-06'
output:
  html_document: default
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r geostatsp, message=FALSE, cache=TRUE}
library('geostatsp')
data("swissRain")
swissRain = terra::unwrap(swissRain)
swissAltitude = terra::unwrap(swissAltitude)
swissRain$elevation = extract(swissAltitude, swissRain)

swissRes =  lgm( formula=rain~ elevation, 
                 data=swissRain, grid=20,
                 covariates=swissAltitude, 
                 reml = FALSE, 
                 fixBoxcox=FALSE, fixShape=FALSE, fixNugget = FALSE,  
                 aniso=TRUE )
swissRes2 =  lgm( formula=rain~ elevation, 
                  data=swissRain, grid=20,
                  covariates=swissAltitude, 
                  reml = FALSE,
                  shape=0.5, 
                  fixBoxcox=FALSE, fixShape=TRUE, fixNugget = FALSE,  
                  aniso=TRUE )
swissRes3 =  lgm( formula=rain~ elevation, 
                  data=swissRain, 
                  grid=20,
                  covariates=swissAltitude, 
                  reml = FALSE,
                  shape=0.9, 
                  fixBoxcox=FALSE, fixShape=TRUE, fixNugget = FALSE,  
                  aniso=TRUE )
swissRes4 =  lgm( formula=rain~ elevation, 
                  data=swissRain, grid=20,
                  covariates=swissAltitude, 
                  reml = FALSE,
                  shape=10,
                  fixBoxcox=FALSE, fixShape=TRUE, fixNugget = FALSE,  
                  aniso=TRUE )
swissRes5 =  lgm( formula=rain~ elevation, 
                  data=swissRain, grid=20,
                  covariates=swissAltitude, 
                  reml = FALSE,
                  shape=20, 
                  fixBoxcox=FALSE, fixShape=TRUE, fixNugget = FALSE,  
                  aniso=TRUE )
swissRes6 =  lgm( formula=rain~ elevation, 
                  data=swissRain, grid=20,
                  covariates=swissAltitude, 
                  reml = FALSE,
                  shape=100, 
                  fixBoxcox=FALSE, fixShape=TRUE, fixNugget = FALSE,  
                  aniso=TRUE )
swissRes$summary[,c('estimate','ci0.05', 'ci0.95')]
swissDataWrap = terra::wrap(swissRes$data)
```

## R Markdown
## Set the parameters
```{r config, message=FALSE, results='hide', cache=FALSE}
library(gpuLik)
alpha1=c(0.00001, 0.01, 0.1, 0.2, 0.25, 0.3, 0.5, 0.8, 0.9, 0.95, 0.99, 0.999)
alpha2=c(0.00001, 0.01, 0.1, 0.2, 0.25, 0.5, 0.8, 0.9, 0.95, 0.99, 0.999)
model_list <- list(swissRes, swissRes2,swissRes3,swissRes4,swissRes5,swissRes6)
A <- gpuLik::configParams(Model = model_list, alpha=alpha1, alphasecond = alpha2,
                          data = terra::unwrap(swissDataWrap))
paramsUse <- A$representativeParamaters
b <- A$boxcox
```

```{r config2,message=FALSE,results='hide', cache=TRUE}
intercept<- sort(c(swissRes$summary['(Intercept)','estimate'], seq(0, 12, len=199)))
cov1  <- sort(c(swissRes$summary['elevation','estimate'], seq(-7, 15, len=199)*1e-04))
Betas <- cbind(intercept, cov1)
sdSpatial <- c(seq(1.2, 5, len=199), swissRes$summary['sdSpatial','estimate'])
```

## Get the profie loglikelihoods and estimates for all model parameters 
```{r onestep, cache=TRUE, eval=TRUE, message=FALSE, fig.show='hide'}
result3<-gpuLik::likfitLgmGpu(model =swissRes,
                         params=paramsUse, 
                         paramToEstimate=c('range','combinedRange','shape','nugget', 
                                           'aniso1', 'aniso2',"anisoRatio", 
                                           "anisoAngleRadians",'boxcox'),
                         boxcox = seq(b[1],b[9],len=33),
                         Betas = Betas,
                         sdSpatial = sdSpatial,
                         cilevel=0.9,  
                         type = "double",
                         convexHullForBetas = FALSE,
                         NparamPerIter=400,
                         Nglobal=c(128,64),
                         Nlocal=c(16,16),
                         NlocalCache=2800,
                         verbose=c(0,0))
```

```{r allestimates, cache=TRUE}
# total parameter configurations for \omega
nrow(paramsUse)
result3$summary
result3$reml
result3$Infindex 
swissRes$optim$logL
max(result3$LogLik)
```

## Or get the profie loglikelihoods step by step
```{r getProfLogL, cache=TRUE, message=FALSE, results='hide'}
result1 <- gpuLik::getProfLogL(data=swissRain,
                                formula=rain~ elevation,
                                coordinates=swissRain@coords,
                                params=paramsUse, 
                                boxcox = seq(b[1],b[9],len=33),
                                type = "double",
                                NparamPerIter=400,
                                gpuElementsOnly = FALSE,
                                reml=FALSE, 
                                Nglobal=c(128,128),
                                Nlocal=c(16,16),
                                NlocalCache=2800,
                                verbose=c(0,0))
```
```{r getproflogL2, cache=TRUE}
# indices of parameter sets that leads to NaN or infinity in Loglikelihood 
result1$Infindex
# total configurations for \lambda
result1$Ndata
# number of observations
result1$Nobs
# number of covariates in the model
result1$Ncov
# predictors in the model
result1$predictors
```

## get the colorful profile plots
```{r correlations}
LogLikcpu = result1$LogLik  # cpu matrix
XVYXVX = result1$XVYXVX  # cpu matrix
ssqResidual = result1$ssqResidual  # cpu matrix
paramToEstimate = c('range','combinedRange',"anisoRatio",
                    'shape','nugget', 'sdNugget', 
                    "anisoAngleRadians", 'aniso1', 
                    'aniso2','boxcox')
cilevel=0.9  # decimal
paramsRenew = result1$paramsRenew 
params = result1$paramsRenew
boxcox = result1$boxcox  
Ndata = result1$Ndata
Nobs = result1$Nobs
Ncov = result1$Ncov
reml = FALSE
predictors = result1$predictors
chisqValue <- qchisq(cilevel,  df = 1)/2
Table <- matrix(NA, nrow=length(paramToEstimate) + Ncov + 1, ncol=3)
rownames(Table) <-  c(predictors, "sdSpatial", paramToEstimate)
colnames(Table) <-  c("estimate", "lci", "uci")
index <- which(LogLikcpu == max(LogLikcpu, na.rm = TRUE), arr.ind = TRUE)
#################sigma hat#########################
if(reml==FALSE)  {
  Table["sdSpatial",1] <- sqrt(ssqResidual[index[1],index[2]]/Nobs)
}else{         
  Table["sdSpatial",1] <- sqrt(ssqResidual[index[1],index[2]]/(Nobs - Ncov))
}
maximum <- max(LogLikcpu)
breaks = maximum - qchisq(cilevel,  df = 1)/2
############### profile for covariance parameters #####################

aniso1 <-  unname(sqrt(paramsRenew[,'anisoRatio']-1) * cos(2*(paramsRenew[,'anisoAngleRadians'])))
aniso2 <-  unname(sqrt(paramsRenew[,'anisoRatio']-1) * sin(2*(paramsRenew[,'anisoAngleRadians'])))
aniso <- cbind(aniso1, aniso2)
sumLogRange <- log(paramsRenew[,'range']^2/paramsRenew[,'anisoRatio'])
combinedRange <- sqrt(paramsRenew[,'range']^2/paramsRenew[,'anisoRatio'])
paramsRenew <- cbind(paramsRenew, sumLogRange, combinedRange, aniso, sqrt(paramsRenew[,"nugget"]) * Table["sdSpatial",1])
colnames(paramsRenew)[ncol(paramsRenew)] <- 'sdNugget'
###################################################
Spars = c("range",'sumLogRange',"combinedRange","nugget",'sdNugget',"shape",
          'aniso1','aniso2','anisoRatio','anisoAngleRadians',"alpha")
result = data.table::as.data.table(cbind(LogLikcpu, paramsRenew[,Spars]))
profileLogLik <- result[, .(profile=max(.SD)), by=Spars]

colAlpha = mapmisc::colourScale(profileLogLik$alpha, style='unique', breaks = 12, col=rainbow, opacity = 0.7)
colAlpha$plot[which(is.na(colAlpha$plot))] = '#000000FF'

profileLogLik[,'profile'] <- profileLogLik[,'profile'] - breaks
profileLogLik <- profileLogLik[profile > maximum- breaks-10]  #maximum- breaks 
profileLogLik <- as.data.frame(profileLogLik)
```


## get the colorful profile plots (continued)
```{r range, fig.show='hold', out.width="49%", cache=TRUE}
plot(profileLogLik$combinedRange, profileLogLik$profile-chisqValue, log='x',cex=.4, xlab="combinedRange",pch=16, ylab="profileLogL", col = colAlpha$plot)
profileLogLik$sumLogRange <- 2*log(profileLogLik$combinedRange)
newdata <- profileLogLik[,c('sumLogRange','profile')]
colnames(newdata)[1]<-"x1"     
datC2 = geometry::convhulln(newdata)
allPoints = unique(as.vector(datC2))
toTest = newdata[allPoints,]
toTest[,'profile'] = toTest[,'profile'] + 0.1
inHull = geometry::inhulln(datC2, as.matrix(toTest))
toUse = newdata[allPoints,][!inHull,]
toTest = newdata[allPoints,]
toUse <- toUse[order(toUse$x1),]
toUse <- head(toUse, - 1)

interp1 = mgcv::gam(profile ~ s(x1, k=nrow(toUse),  m=1, fx=TRUE), data=toUse)
profsumLogRange = data.frame(x1=seq(min(toUse$x1), max(toUse$x1), len=1001))
profsumLogRange$z = predict(interp1, profsumLogRange)

points(exp(0.5*toTest[,1]), toTest[,2]-chisqValue, col='red', cex=0.6)
points(exp(0.5*toUse[,1]), toUse[,2]-chisqValue, col='blue', cex=0.6, pch=3)
lines(exp(0.5*profsumLogRange$x1), profsumLogRange$z-chisqValue, col = 'green')
abline(h =-chisqValue, lty = 2, col='black')
lower = min(newdata$x1)
upper = max(newdata$x1)
f1 <- approxfun(toUse[,1], toUse[,2])
MLE <- sqrt(paramsRenew[index[1],'range']^2/paramsRenew[index[1],'anisoRatio'])
ci<-rootSolve::uniroot.all(f1, lower = lower, upper = upper)
abline(v =c(MLE,exp(0.5*ci)), lty = 2, col='black')



## shape
plot(profileLogLik$shape, profileLogLik$profile-chisqValue, cex=.2, xlab="shape", ylab="profileLogL",  log='x', col = colAlpha$plot)
profileLogLik$logshape <- log(profileLogLik$shape)
newdata <- profileLogLik[,c('logshape','profile')]
colnames(newdata)[1]<-"x1"

datC2 = geometry::convhulln(newdata)
allPoints = unique(as.vector(datC2))
toTest = newdata[allPoints,]
toTest[,'profile'] = toTest[,'profile'] + 0.1
inHull = geometry::inhulln(datC2, as.matrix(toTest))
toUse = newdata[allPoints,][!inHull,]
toTest = newdata[allPoints,]
toUse <- toUse[order(toUse$x1),]
points(exp(toTest[,1]),toTest[,2]-chisqValue, col='red', cex=0.6)
points(exp(toUse[,1]), toUse[,2]-chisqValue, col='blue', cex=0.6, pch=3)
interp1 = mgcv::gam(profile ~ s(x1, k=nrow(toUse),  m=1, fx=TRUE), data=toUse)
profShapeLog = data.frame(x1=seq(min(toUse$x1), max(toUse$x1), len=1001))
profShapeLog$z = predict(interp1, profShapeLog)

lines(exp(profShapeLog$x1), profShapeLog$z-chisqValue, col = 'green')
abline(h =-chisqValue, lty = 2, col='black') 
f1 <- approxfun(toUse[,1], toUse[,2])

lower = min(toUse$x1)
upper = max(toUse$x1)
MLE <- paramsRenew[index[1],'shape']
ci<-rootSolve::uniroot.all(f1, lower = lower, upper = upper)
abline(v =c(MLE,exp(ci)), lty = 2, col='black')


## nugget
plot(profileLogLik$nugget, profileLogLik$profile-chisqValue, cex=.2, xlab="nugget", ylab="profileLogL", col = colAlpha$plot)
profileLogLik2 <- profileLogLik[,c('nugget','profile')]
colnames(profileLogLik2) <- c("x1", 'profile')
datC2 = geometry::convhulln(profileLogLik2)
allPoints = unique(as.vector(datC2))
toTest = profileLogLik2[allPoints,]
toTest[,'profile'] = toTest[,'profile'] + 0.1
inHull = geometry::inhulln(datC2, as.matrix(toTest))
toUse = profileLogLik2[allPoints,][!inHull,]
toTest = profileLogLik2[allPoints,]
toUse <- toUse[order(toUse$x1),]
points(toTest[,1], toTest[,2]-chisqValue, col='red', cex=0.6)
points(toUse[,1], toUse[,2]-chisqValue, col='blue', cex=0.6, pch=3)

interp1 = mgcv::gam(profile ~ s(x1, k=nrow(toUse), m=1, fx=TRUE), data=toUse)
profNugget = data.frame(x1=seq(min(toUse$x1), max(toUse$x1), len=1001))
profNugget$z = predict(interp1, profNugget)
lines(profNugget$x1, profNugget$z-chisqValue, col = 'green')
abline(h =-chisqValue, lty = 2, col='black')

lower = min(profileLogLik2$x1)
upper = max(profileLogLik2$x1)
f1 <- approxfun(toUse[,1], toUse[,2])
MLE <- paramsRenew[index[1],'nugget']
ci<-rootSolve::uniroot.all(f1, lower = lower, upper = upper)
abline(v =c(MLE,ci), lty = 2,  col='black')


## aniso1
plot(profileLogLik$aniso1, profileLogLik$profile-chisqValue, cex=.2, xlab="aniso1", ylab="profileLogL", col = colAlpha$plot)
profileLogLik2 <- profileLogLik[,c('aniso1','profile')]
colnames(profileLogLik2) <- c("x1", 'profile')
datC2 = geometry::convhulln(profileLogLik2)
allPoints = unique(as.vector(datC2))
toTest = profileLogLik2[allPoints,]
toTest[,'profile'] = toTest[,'profile'] + 0.1
inHull = geometry::inhulln(datC2, as.matrix(toTest))
toUse = profileLogLik2[allPoints,][!inHull,]
toTest = profileLogLik2[allPoints,]
toUse <- toUse[order(toUse$x1),]
toUse <- head(toUse, - 1)
points(toTest[,1], toTest[,2]-chisqValue, col='red', cex=0.6)
points(toUse[,1], toUse[,2]-chisqValue, col='blue', cex=0.6, pch=3)

interp1 = mgcv::gam(profile ~ s(x1, k=nrow(toUse), m=1, fx=TRUE), data=toUse)
profaniso1 = data.frame(x1=seq(min(toUse$x1), max(toUse$x1), len=1001))
profaniso1$z = predict(interp1, profaniso1)
lines(profaniso1$x1, profaniso1$z-chisqValue, col = 'green')

abline(h =-chisqValue, lty = 2, col='black')
lower = min(profaniso1$x1)
upper = max(profaniso1$x1)
f1 <- approxfun(toUse[,1], toUse[,2])
MLE <- sqrt(paramsRenew[index[1],'anisoRatio']-1) * cos(2*(paramsRenew[index[1],'anisoAngleRadians']))
ci<-rootSolve::uniroot.all(f1, lower = lower, upper = upper)
abline(v =c(MLE,ci), lty = 2, col='black')


## aniso2
plot(profileLogLik$aniso2, profileLogLik$profile-chisqValue, cex=.2, xlab="aniso2", ylab="profileLogL", col = colAlpha$plot)
profileLogLik3 <- profileLogLik[,c('aniso2','profile')]
colnames(profileLogLik3) <- c("x1", 'profile')
datC2 = geometry::convhulln(profileLogLik3)
allPoints = unique(as.vector(datC2))
toTest = profileLogLik3[allPoints,]
toTest[,'profile'] = toTest[,'profile'] + 0.1
inHull = geometry::inhulln(datC2, as.matrix(toTest))
toUse = profileLogLik3[allPoints,][!inHull,]
toTest = profileLogLik3[allPoints,]
toUse <- toUse[order(toUse$x1),]
toUse <- head(toUse, - 1)
points(toTest[,1], toTest[,2]-chisqValue, col='red', cex=0.6)
points(toUse[,1], toUse[,2]-chisqValue, col='blue', cex=0.6, pch=3)

interp1 = mgcv::gam(profile ~ s(x1, k=nrow(toUse), m=1, fx=TRUE), data=toUse)
profaniso2 = data.frame(x1=seq(min(toUse$x1), max(toUse$x1), len=1001))
profaniso2$z = predict(interp1, profaniso2)
lines(profaniso2$x1, profaniso2$z-chisqValue, col = 'green')
abline(h =-chisqValue, lty = 2, col='black')
lower = min(profileLogLik3$x1)
upper = max(profileLogLik3$x1)

f1 <- approxfun(toUse[,1], toUse[,2])
MLE <- sqrt(paramsRenew[index[1],'anisoRatio']-1) * sin(2*(paramsRenew[index[1],'anisoAngleRadians']))
ci<-rootSolve::uniroot.all(f1, lower = lower, upper = upper)
abline(v =c(MLE,ci), lty = 2, col='black')


## boxcox
likForboxcox = cbind(boxcox, apply(LogLikcpu, 2,  max) )
f1 <- approxfun(likForboxcox[,1], likForboxcox[,2]-breaks)
plot(likForboxcox[,1], likForboxcox[,2]-breaks-chisqValue, ylab= "proLogL", xlab='Box-Cox', cex=0.5)
likForboxcox <- likForboxcox[order(likForboxcox[,1]),]
lines(likForboxcox[,1], likForboxcox[,2]-breaks-chisqValue, col='blue')
abline(h =-chisqValue, lty = 2)

lower = min(boxcox)
upper = max(boxcox)
ci<-rootSolve::uniroot.all(f1, lower = lower, upper = upper)
abline(v =c(boxcox[index[2]],ci), lty = 2)

```











# Do it step by step
## get estimates for correlation parameters 
```{r 1, eval=FALSE}
result2<-gpuLik::prof1dCov(LogLik = result1$LogLik,  # cpu matrix
                   XVYXVX = result1$XVYXVX,  # cpu matrix
                   ssqResidual = result1$ssqResidual,  # cpu matrix
                   paramToEstimate = c('range','combinedRange','shape', 
                                       'nugget','aniso1', 'aniso2','boxcox'),
                   cilevel=0.9, 
                   params = result1$paramsRenew, 
                   boxcox = result1$boxcox,  
                   Ndata = result1$Ndata,
                   Nobs = result1$Nobs,
                   Ncov = result1$Ncov,
                   reml = FALSE,
                   predictors = result1$predictors,  # character string
                   verbose=FALSE)

# table of estimates
result2$summary
# index for the MLE parameter set
result2$mleIndex

```

# get estimates and profile plots for betas'
```{r beta_profile, eval=TRUE, out.width="49%", cache=TRUE}
intercept<- sort(c(swissRes$summary['(Intercept)','estimate'], seq(0, 12, len=199)))
elevation  <- sort(c(swissRes$summary['elevation','estimate'], seq(-7, 15, len=199)*1e-04))
Betas <- cbind(intercept, elevation)

output<-gpuLik::Prof1dBetas(Betas=Betas,
                            cilevel=0.9,
                            Nobs = result1$Nobs,
                            Ndata = result1$Ndata,
                            Nparam = result1$Nparam,
                            Ncov = result1$Ncov,
                            detVar = result1$detVar,
                            result1$detReml,
                            result1$ssqY,   
                            result1$XVYXVX,   
                            result1$jacobian,
                            convexHull = FALSE)

output$estimates
output$breaks
```



# estimates and profile plots for sdSpatial
```{r sdSpatial, eval=TRUE, cache=TRUE, fig.show='hide'}
sdSpatial <- sort(c(seq(1.2, 5, len=39), swissRes$summary['sdSpatial','estimate']))
provarresult <- gpuLik::profVariance(sdSpatial, 
             cilevel=0.9,
             result1$Nobs, 
             result1$Ndata,
             result1$Nparam,
             result1$Ncov,
             result1$detVar, 
             result1$detReml, 
             result1$ssqResidual, 
             result1$jacobian)

provarresult$estimates
breaks <- provarresult$breaks

temp <- qchisq(cilevel,  df = 1)/2
LogLik <- provarresult$LogLik
```

```{r sdSpatial2, eval=TRUE, cache=TRUE}
plot(sdSpatial,LogLik-breaks-temp, cex=0.6, ylab='profileLogL')
lines(sdSpatial,LogLik-breaks-temp, col='blue')
abline(h=-temp, lty = 2)

abline(v=provarresult$estimates[c(1,2,3)], lty = 2)
text(provarresult$estimates[1], -3.7, round(provarresult$estimates[1],digits = 2))
text(provarresult$estimates[2], -3.7, round(provarresult$estimates[2],digits = 2))
text(provarresult$estimates[3], -3.7, round(provarresult$estimates[3],digits = 2))
```


## 2D profile plots
```{r 2dplotsprep, cache=TRUE}
Spars = c("range",'sumLogRange',"combinedRange","nugget",'sdNugget',"shape",'aniso1','aniso2','anisoRatio','anisoAngleRadians',"alpha")
result = data.table::as.data.table(cbind(LogLikcpu, paramsRenew[,Spars]))
profileLogLik <- result[, .(profile=max(.SD)), by=Spars]
head(profileLogLik)


profileLogLik[,'profile'] <- profileLogLik[,'profile'] -maximum
profileLogLik <- profileLogLik[profile > -10]  
profileLogLik$logshape <- log(profileLogLik$shape)
profileLogLik <- as.data.frame(profileLogLik)

```


```{r  sumLogRangenugget}
profileLogL <- profileLogLik[,c('sumLogRange','nugget','profile')]
datC2 = geometry::convhulln(profileLogL)
allPoints2 = unique(as.vector(datC2))
toTest2 = profileLogL[allPoints2,]
toTest2[,'profile'] = toTest2[,'profile'] - 0.1
inHull2 = geometry::inhulln(datC2, as.matrix(toTest2))
toUse2 = profileLogL[allPoints2,][inHull2,]
toTest2 = profileLogL[allPoints2,]

Sprob = c(0, 0.1, 0.2, 0.5, 0.8, 0.95, 0.99, 0.999, 1) 
Sbreaks =qchisq(Sprob, df=2)/2
Sbreaks = pmin(Sbreaks, 1000)
Sbreaks[1] = -10
SbreaksC = rev(- Sbreaks)
colDat2 = mapmisc::colourScale(profileLogL[,'profile'], style='fixed',
                               breaks=SbreaksC, 
                               col='Spectral', rev=TRUE)

interp2 = mgcv::gam(profile ~ s(sumLogRange, nugget, k=16, m=3,fx=TRUE), data=toUse2)
prof2list = list(sumLogRange=seq(15, 23, len=301),
                 nugget=seq(0, 0.6, len=301))
prof2 = do.call(expand.grid, prof2list)
prof2$z = predict(interp2, prof2)

col2 = mapmisc::colourScale(as.vector(prof2[,'z']), breaks=SbreaksC, col=colDat2$col, style='fixed')
colPoints = mapmisc::colourScale(toUse2[,'profile'], breaks=SbreaksC, col=col2$col, style='fixed')


plot(prof2[,c('sumLogRange','nugget')], col=col2$plot, pch=15)
points(toUse2[,c('sumLogRange','nugget')], col='black', cex=0.8)
mapmisc::legendBreaks('topright', breaks = rev(Sprob), col=colDat2$col)
```


```{r  rangevsshape}
profileLogL <- profileLogLik[ , c('sumLogRange','logshape', 'shape',  'profile')]

transFun = function(xx) xx^(-0.5)
invTransFun = function(xx) xx^(-2)

Sprob = c(0, 0.1, 0.2, 0.5, 0.8, 0.95, 0.99, 0.999, 1) 
Sbreaks =qchisq(Sprob, df=2)/2
Sbreaks = pmin(Sbreaks, 1000)
Sbreaks[1] = -10
SbreaksC = rev(-Sbreaks)
colDat2 = mapmisc::colourScale(profileLogL[,'profile'], style='fixed',
                               breaks=SbreaksC, 
                               col='Spectral', rev=TRUE)

Sshape = c(0.1, 1/4, 0.5, 1, 2, 5, 10, 100)

profForChull = cbind(
  sumLogRange = profileLogL$sumLogRange,
  shapeTrans = transFun(profileLogL$shape),
  profile=profileLogL$profile)


theHull = geometry::convhulln(profForChull)
toTest = profForChull[as.vector(theHull), ]
toTest[,'profile'] = toTest[,'profile'] - 0.1
inHull = geometry::inhulln(theHull, as.matrix(toTest))
toUse = toTest[inHull,]
toUse2 =  toUse[!duplicated(toUse[,c('sumLogRange','shapeTrans')]), ]


if(TRUE) {
  profForChullSub = profForChull[profileLogL$shape > 1 & profileLogL$shape < 8, ]
  theHullSub = geometry::convhulln(profForChullSub)
  toTestSub = profForChullSub[as.vector(theHullSub), ]
  toTestSub[,'profile'] = toTestSub[,'profile'] - 0.1
  inHullSub = geometry::inhulln(theHullSub, as.matrix(toTestSub))
  toUseSub = toTestSub[inHullSub,]
  toUse2 = rbind(toUse, toUseSub)
  toUse2 = toUse2[!duplicated(toUse2[,c('sumLogRange','shapeTrans')]), ]
}

theGridList = list(sumLogRange = seq(15, 23.3, len=201),
                   logshape = seq(-1.78, 4.6, len=201))
theGrid = do.call(expand.grid, theGridList)

theInterp = akima::interp(
  toUse2[,'sumLogRange'], toUse2[,'shapeTrans'], toUse2[,'profile'],
  theGridList$sumLogRange,
  transFun(exp(theGridList$logshape)),
  extrap=FALSE, linear=TRUE)


col2 = mapmisc::colourScale(as.vector(theInterp$z), breaks=SbreaksC, col=colDat2$col, style='fixed')
colPoints = mapmisc::colourScale(toUse2[,'profile'], breaks=SbreaksC, col=col2$col, style='fixed')

plot(theGrid[,'sumLogRange'],theGrid[,'logshape'], col=col2$plot, pch=15, ylab='logshape', xlab='sumLogRange')
points(toUse2[,'sumLogRange'], log(invTransFun(toUse2[, 'shapeTrans'])), cex=0.8)
```













