---
title: "swissrain data code"
author: "ruoyong"
date: "2023-12-14"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```


## R Markdown
## Get MLE’s of parameters
```{r geostatsp, message=FALSE, cache=TRUE}
library('geostatsp')
data("swissRain")
swissRain = terra::unwrap(swissRain)
swissAltitude = terra::unwrap(swissAltitude)
swissRain$elevation = terra::extract(swissAltitude, swissRain, ID=FALSE)

swissRes =  lgm( formula=rain~ elevation, 
                 data=swissRain, grid=20,
                 covariates=swissAltitude, 
                 reml = FALSE, 
                 fixBoxcox=FALSE, fixShape=FALSE, fixNugget = FALSE,  
                 aniso=TRUE )
swissRes2 =  lgm( formula=rain~ elevation, 
                  data=swissRain, grid=20,
                  covariates=swissAltitude, 
                  reml = FALSE,
                  shape=0.5, 
                  fixBoxcox=FALSE, fixShape=TRUE, fixNugget = FALSE,  
                  aniso=TRUE )
swissRes3 =  lgm( formula=rain~ elevation, 
                  data=swissRain, 
                  grid=20,
                  covariates=swissAltitude, 
                  reml = FALSE,
                  shape=0.9, 
                  fixBoxcox=FALSE, fixShape=TRUE, fixNugget = FALSE,  
                  aniso=TRUE )
swissRes4 =  lgm( formula=rain~ elevation, 
                  data=swissRain, grid=20,
                  covariates=swissAltitude, 
                  reml = FALSE,
                  shape=10,
                  fixBoxcox=FALSE, fixShape=TRUE, fixNugget = FALSE,  
                  aniso=TRUE )
swissRes5 =  lgm( formula=rain~ elevation, 
                  data=swissRain, grid=20,
                  covariates=swissAltitude, 
                  reml = FALSE,
                  shape=20, 
                  fixBoxcox=FALSE, fixShape=TRUE, fixNugget = FALSE,  
                  aniso=TRUE )
swissRes6 =  lgm( formula=rain~ elevation, 
                  data=swissRain, grid=20,
                  covariates=swissAltitude, 
                  reml = FALSE,
                  shape=100, 
                  fixBoxcox=FALSE, fixShape=TRUE, fixNugget = FALSE,  
                  aniso=TRUE )
swissRes$summary[,c('estimate','ci0.05', 'ci0.95')]
swissDataWrap = terra::wrap(swissRes$data)
```

## Set the representative parameters 
```{r config, message=FALSE, results='hide', cache=FALSE}
library('gpuR')
setContext(grep("gpu", listContexts()$device_type)[1])
library(gpuLik)
alpha1=c(0.00001, 0.01, 0.1, 0.2, 0.25, 0.3, 0.5, 0.8, 0.9, 0.95, 0.99, 0.999)
alpha2=c(0.00001, 0.01, 0.1, 0.2, 0.25, 0.5, 0.8, 0.9, 0.95, 0.99, 0.999)
model_list <- list(swissRes, swissRes2,swissRes3,swissRes4,swissRes5,swissRes6)
A <- configParams(Model = model_list, alpha=alpha1, alphasecond = alpha2,
                          data = terra::unwrap(swissDataWrap))
paramsUse <- A$representativeParamaters
b <- A$boxcox
```

```{r config2,message=FALSE,results='hide', cache=FALSE}
intercept<- sort(c(swissRes$summary['(Intercept)','estimate'], seq(0, 12, len=199)))
cov1  <- sort(c(swissRes$summary['elevation','estimate'], seq(-7, 15, len=199)*1e-04))
Betas <- cbind(intercept, cov1)
sdSpatial <- c(seq(1.2, 5, len=199), swissRes$summary['sdSpatial','estimate'])
```

## Get the profie loglikelihoods and estimates for all model parameters on GPU in one step,
## change verbose argument if you would like to see backend code information
```{r onestep, cache=FALSE, eval=TRUE, message=FALSE, fig.show='hide'}
result<-gpuLik::likfitLgmGpu(model =swissRes,
                         params=paramsUse, 
                         data = terra::unwrap(swissDataWrap), 
                         paramToEstimate=c('range','combinedRange','shape','nugget', 
                                           'aniso1', 'aniso2',"anisoRatio", 
                                           "anisoAngleRadians",'boxcox'),
                         boxcox = seq(b[1],b[9],len=33),
                         Betas = Betas,
                         sdSpatial = sdSpatial,
                         cilevel=0.9,  
                         type = "double",
                         convexHullForBetas = FALSE,
                         NparamPerIter=256,
                         Nglobal=c(64,64),
                         Nlocal=c(8,8),
                         NlocalCache=2000,
                         verbose=0)
```
```{r checkProfIntercept}
stuff = gpuLik::getProfLogL(data=terra::unwrap(swissDataWrap),
           formula=swissRes$model$formula,
           coordinates=crds(terra::unwrap(swissDataWrap)),
           params=paramsUse, 
           boxcox = seq(b[1],b[9],len=31),
           type = "double",
           NparamPerIter=256,
           gpuElementsOnly = FALSE,
           reml=FALSE, 
           Nglobal=c(64,64),    
           Nlocal=c(16, 8),
           NlocalCache=2000,
           verbose=c(1,0))
max(stuff$LogLik)
swissRes$opt$logL
#output<-gpuLik::Prof1dBetas(
  Betas=Betas
                            cilevel=0.95
                            Nobs = stuff$Nobs
                            Ndata = stuff$Ndata
                            Nparam = stuff$Nparam
                            Ncov = stuff$Ncov
                            detVar = stuff$detVar
                            detReml = stuff$detReml
                            ssqY = stuff$ssqY
                            XVYXVX = stuff$XVYXVX
                            jacobian = stuff$jacobian
                            reml=FALSE
                            convexHull = FALSE
  m <- nrow(Betas)
  detVar <- matrix(rep(detVar, Ndata), nrow=Nparam)
  jacobian <- do.call(rbind, replicate(Nparam, jacobian, simplify = FALSE))
  #dim(XVYXVX)
  Ucov <- Ncov-1
  XTVinvX <- XVYXVX[ , (ncol(XVYXVX)-Ncov+1):ncol(XVYXVX)]
  XVY <- matrix(XVYXVX[ , 1:Ndata], ncol=Ndata)
  
  #dim(XTVinvX)
  ## make each symmetric
  for (i in 1:Nparam){
    XTVinvX[((i-1)*Ncov+1) : (i*Ncov), ] <- gpuLik:::makeSymm(XTVinvX[((i-1)*Ncov+1) : (i*Ncov), ])
  }

  LogLik_optimized = matrix(0, nrow=m, ncol=ncol(Betas))
  #breaks <- rep(0, ncol(Betas))
  Table <- matrix(NA, nrow=ncol(Betas), ncol=4)
  colnames(Table) <-  c("MLE", paste(c('lower', 'upper'), cilevel*100, 'ci', sep = ''),"maximum")
  rownames(Table) <- colnames(Betas)
  #index <- matrix(0, nrow=m, ncol=2)
  profBetas <- matrix(0, nrow=1001, ncol=2*ncol(Betas))
  
a=1
      BetaSlice <- Betas[,a]
  selectedrows <- (seq_len(Nparam)-1) * Ncov + a
  XTVinvX_deleted <- XTVinvX[-selectedrows,-a,drop=FALSE]
  XTVinvX_a <-  XTVinvX[-selectedrows, a,drop=FALSE]
  XVY_deleted <- XVY[-selectedrows, ,drop=FALSE]
  X_aVY <- XVY[selectedrows, ,drop=FALSE]
  X_aVX_a <- XTVinvX[selectedrows, a, drop=FALSE]
  
  partA =  
  partB = 
  partC =  
  partD =  
  partE = matrix(0, nrow=Nparam, ncol=Ndata)
  
  
   for (i in 1:Nparam){
      interval <- c(((i-1)*Ucov+1) : (i*Ucov))
      temp <- solve(XTVinvX_deleted[interval, ]) 
      if(Ucov==1){
        #diag(XVY_deleted[interval,] %*% temp  %*% XVY_deleted[interval,])
        partA[i,] = rowSums(XVY_deleted[interval,] %*% temp * XVY_deleted[interval,])
        # part (B) have 2 data sets.   has beta
        partB[i,] = -(XTVinvX_a[interval,]) %*% temp %*% XVY_deleted[interval,]
        # part (C) no data sets.  has beta
        partC[i,] = XTVinvX_a[interval, ] %*% temp %*% XTVinvX_a[interval, ]
        # part (D) have 2 data sets.    has beta
        partD[i,] = - X_aVY[i, ]
        # part (E)
        partE[i,] = X_aVX_a[i]
      }else{
        #diag(t(XVY_deleted[interval,]) %*% temp %*% XVY_deleted[interval,])
        # part (A) have 2 data sets
        partA[i,] = rowSums(t(XVY_deleted[interval,]) %*% temp * t(XVY_deleted[interval,]))
        # part (B) have 2 data sets.   has beta
        partB[i,] = -(XTVinvX_a[interval,]) %*% temp %*% XVY_deleted[interval,]
        # part (C) no data sets.  has beta
        partC[i,] = XTVinvX_a[interval, ] %*% temp %*% XTVinvX_a[interval, ]
        # part (D) have 2 data sets.    has beta
        partD[i,] = - X_aVY[i, ]
        # part (E)
        partE[i,] = X_aVX_a[i]
      }
    }
       
bet= which(BetaSlice == swissRes$parameters['(Intercept)'])

stuff2 = 2* BetaSlice[bet] *partD + BetaSlice[bet]^2 *partE - (partA + 2*BetaSlice[bet]* partB + BetaSlice[bet]^2 * partC)

      ssqResidual <- ssqY + stuff2
        
        loglik_forthisbeta <- (-0.5)*(Nobs*log(ssqResidual/Nobs) + detVar + Nobs + Nobs*log(2*pi) + jacobian)

    max(loglik_forthisbeta)
    swissRes$opt$logL
      
    loglik_forthisbeta[1,which(boxcox==swissRes$parameters['boxcox'])]
  
    
                         
stuff2 =   2*BetaSlice[bet]*  partD + BetaSlice[bet]^2 * partE - 
   (partA + 2*BetaSlice[bet] * partB + BetaSlice[bet]^2 * partC)            
    
stuff2[1,which(boxcox==swissRes$parameters['boxcox'])]
stuff$ssqBetahat[1, which(boxcox==swissRes$parameters['boxcox'])]                  

rbind(output$estimates[,1:3],
as.matrix(swissRes$summary[1:2,c(1,5,6)]))
```


## Show the results
```{r allestimates, cache=FALSE}
# total parameter configurations for \omega
nrow(paramsUse)
result$summary
result$reml
result$Infindex 
swissRes$optim$logL
max(result$LogLik)
```

## Alternatively, we can get the estimates step by step
## Step 1, get the profie loglikelihoods for correlation and BoxCox parameters
```{r getProfLogL, cache=FALSE, message=FALSE, results='hide'}
result_1 <- gpuLik::getProfLogL(data = terra::unwrap(swissDataWrap), 
                               formula=rain~ elevation,
                               coordinates=terra::crds(swissRain),
                               params=paramsUse, 
                               boxcox = seq(b[1],b[9],len=33),
                               type = "double",
                               NparamPerIter=256,
                               gpuElementsOnly = FALSE,
                               reml=FALSE, 
                               Nglobal=c(64,64),
                               Nlocal=c(16,8),
                               NlocalCache=2000,
                               verbose=c(0,0))
```


## Show some results
```{r getproflogL2, cache=TRUE}
# indices of parameter sets that leads to NaN or infinity in Loglikelihood 
result_1$Infindex
# total configurations for \lambda
result_1$Ndata
# number of observations
result_1$Nobs
# number of covariates in the model
result_1$Ncov
# predictors in the model
result_1$predictors
```

## Get colorful profile likelihoods plots (setup)
```{r correlations}
LogLikcpu = result_1$LogLik  # cpu matrix
XVYXVX = result_1$XVYXVX  # cpu matrix
ssqResidual = result_1$ssqResidual  # cpu matrix
paramToEstimate = c('range','combinedRange',"anisoRatio",
                    'shape','nugget', 'sdNugget', 
                    "anisoAngleRadians", 'aniso1', 
                    'aniso2','boxcox')
cilevel=0.9  # decimal
paramsRenew = result_1$paramsRenew 
params = result_1$paramsRenew
boxcox = result_1$boxcox  
Ndata = result_1$Ndata
Nobs = result_1$Nobs
Ncov = result_1$Ncov
reml = FALSE
predictors = result_1$predictors
chisqValue <- qchisq(cilevel,  df = 1)/2
Table <- matrix(NA, nrow=length(paramToEstimate) + Ncov + 1, ncol=3)
rownames(Table) <-  c(predictors, "sdSpatial", paramToEstimate)
colnames(Table) <-  c("estimate", "lci", "uci")
index <- which(LogLikcpu == max(LogLikcpu, na.rm = TRUE), arr.ind = TRUE)
#################sigma hat#########################
if(reml==FALSE)  {
  Table["sdSpatial",1] <- sqrt(ssqResidual[index[1],index[2]]/Nobs)
}else{         
  Table["sdSpatial",1] <- sqrt(ssqResidual[index[1],index[2]]/(Nobs - Ncov))
}
maximum <- max(LogLikcpu)
breaks = maximum - qchisq(cilevel,  df = 1)/2
############### profile for covariance parameters #####################

aniso1 <-  unname(sqrt(paramsRenew[,'anisoRatio']-1) * cos(2*(paramsRenew[,'anisoAngleRadians'])))
aniso2 <-  unname(sqrt(paramsRenew[,'anisoRatio']-1) * sin(2*(paramsRenew[,'anisoAngleRadians'])))
aniso <- cbind(aniso1, aniso2)
sumLogRange <- log(paramsRenew[,'range']^2/paramsRenew[,'anisoRatio'])
combinedRange <- sqrt(paramsRenew[,'range']^2/paramsRenew[,'anisoRatio'])
paramsRenew <- cbind(paramsRenew, sumLogRange, combinedRange, aniso, sqrt(paramsRenew[,"nugget"]) * Table["sdSpatial",1])
colnames(paramsRenew)[ncol(paramsRenew)] <- 'sdNugget'
###################################################
Spars = c("range",'sumLogRange',"combinedRange","nugget",'sdNugget',"shape",
          'aniso1','aniso2','anisoRatio','anisoAngleRadians',"alpha")
result = data.table::as.data.table(cbind(LogLikcpu, paramsRenew[,Spars]))
profileLogLik <- result[, .(profile=max(.SD)), by=Spars]

colAlpha = mapmisc::colourScale(profileLogLik$alpha, style='unique', breaks = 12, col=rainbow, opacity = 0.7)
colAlpha$plot[which(is.na(colAlpha$plot))] = '#000000FF'

profileLogLik[,'profile'] <- profileLogLik[,'profile'] - breaks
profileLogLik <- profileLogLik[profile > maximum- breaks-10]  #maximum- breaks 
profileLogLik <- as.data.frame(profileLogLik)
```


## Get the colorful profile plots for covariance and BoxCox parameters
```{r range, fig.show='hold', out.width="49%", cache=TRUE}
plot(profileLogLik$combinedRange, profileLogLik$profile-chisqValue, log='x',cex=.4, xlab="combinedRange",pch=16, ylab="profileLogL", col = colAlpha$plot)
profileLogLik$sumLogRange <- 2*log(profileLogLik$combinedRange)
newdata <- profileLogLik[,c('sumLogRange','profile')]
colnames(newdata)[1]<-"x1"     
datC2 = geometry::convhulln(newdata)
allPoints = unique(as.vector(datC2))
toTest = newdata[allPoints,]
toTest[,'profile'] = toTest[,'profile'] + 0.1
inHull = geometry::inhulln(datC2, as.matrix(toTest))
toUse = newdata[allPoints,][!inHull,]
toTest = newdata[allPoints,]
toUse <- toUse[order(toUse$x1),]
toUse <- head(toUse, - 1)

interp1 = mgcv::gam(profile ~ s(x1, k=nrow(toUse),  m=1, fx=TRUE), data=toUse)
profsumLogRange = data.frame(x1=seq(min(toUse$x1), max(toUse$x1), len=1001))
profsumLogRange$z = predict(interp1, profsumLogRange)

points(exp(0.5*toTest[,1]), toTest[,2]-chisqValue, col='red', cex=0.6)
points(exp(0.5*toUse[,1]), toUse[,2]-chisqValue, col='blue', cex=0.6, pch=3)
lines(exp(0.5*profsumLogRange$x1), profsumLogRange$z-chisqValue, col = 'green')
abline(h =-chisqValue, lty = 2, col='black')
lower = min(newdata$x1)
upper = max(newdata$x1)
f1 <- approxfun(toUse[,1], toUse[,2])
MLE <- sqrt(paramsRenew[index[1],'range']^2/paramsRenew[index[1],'anisoRatio'])
ci<-rootSolve::uniroot.all(f1, lower = lower, upper = upper)
abline(v =c(MLE,exp(0.5*ci)), lty = 2, col='black')



## shape
plot(profileLogLik$shape, profileLogLik$profile-chisqValue, cex=.2, xlab="shape", ylab="profileLogL",  log='x', col = colAlpha$plot)
profileLogLik$logshape <- log(profileLogLik$shape)
newdata <- profileLogLik[,c('logshape','profile')]
colnames(newdata)[1]<-"x1"

datC2 = geometry::convhulln(newdata)
allPoints = unique(as.vector(datC2))
toTest = newdata[allPoints,]
toTest[,'profile'] = toTest[,'profile'] + 0.1
inHull = geometry::inhulln(datC2, as.matrix(toTest))
toUse = newdata[allPoints,][!inHull,]
toTest = newdata[allPoints,]
toUse <- toUse[order(toUse$x1),]
points(exp(toTest[,1]),toTest[,2]-chisqValue, col='red', cex=0.6)
points(exp(toUse[,1]), toUse[,2]-chisqValue, col='blue', cex=0.6, pch=3)
interp1 = mgcv::gam(profile ~ s(x1, k=nrow(toUse),  m=1, fx=TRUE), data=toUse)
profShapeLog = data.frame(x1=seq(min(toUse$x1), max(toUse$x1), len=1001))
profShapeLog$z = predict(interp1, profShapeLog)

lines(exp(profShapeLog$x1), profShapeLog$z-chisqValue, col = 'green')
abline(h =-chisqValue, lty = 2, col='black') 
f1 <- approxfun(toUse[,1], toUse[,2])

lower = min(toUse$x1)
upper = max(toUse$x1)
MLE <- paramsRenew[index[1],'shape']
ci<-rootSolve::uniroot.all(f1, lower = lower, upper = upper)
abline(v =c(MLE,exp(ci)), lty = 2, col='black')


## nugget
plot(profileLogLik$nugget, profileLogLik$profile-chisqValue, cex=.2, xlab="nugget", ylab="profileLogL", col = colAlpha$plot)
profileLogLik2 <- profileLogLik[,c('nugget','profile')]
colnames(profileLogLik2) <- c("x1", 'profile')
datC2 = geometry::convhulln(profileLogLik2)
allPoints = unique(as.vector(datC2))
toTest = profileLogLik2[allPoints,]
toTest[,'profile'] = toTest[,'profile'] + 0.1
inHull = geometry::inhulln(datC2, as.matrix(toTest))
toUse = profileLogLik2[allPoints,][!inHull,]
toTest = profileLogLik2[allPoints,]
toUse <- toUse[order(toUse$x1),]
points(toTest[,1], toTest[,2]-chisqValue, col='red', cex=0.6)
points(toUse[,1], toUse[,2]-chisqValue, col='blue', cex=0.6, pch=3)

interp1 = mgcv::gam(profile ~ s(x1, k=nrow(toUse), m=1, fx=TRUE), data=toUse)
profNugget = data.frame(x1=seq(min(toUse$x1), max(toUse$x1), len=1001))
profNugget$z = predict(interp1, profNugget)
lines(profNugget$x1, profNugget$z-chisqValue, col = 'green')
abline(h =-chisqValue, lty = 2, col='black')

lower = min(profileLogLik2$x1)
upper = max(profileLogLik2$x1)
f1 <- approxfun(toUse[,1], toUse[,2])
MLE <- paramsRenew[index[1],'nugget']
ci<-rootSolve::uniroot.all(f1, lower = lower, upper = upper)
abline(v =c(MLE,ci), lty = 2,  col='black')


## aniso1
plot(profileLogLik$aniso1, profileLogLik$profile-chisqValue, cex=.2, xlab="aniso1", ylab="profileLogL", col = colAlpha$plot)
profileLogLik2 <- profileLogLik[,c('aniso1','profile')]
colnames(profileLogLik2) <- c("x1", 'profile')
datC2 = geometry::convhulln(profileLogLik2)
allPoints = unique(as.vector(datC2))
toTest = profileLogLik2[allPoints,]
toTest[,'profile'] = toTest[,'profile'] + 0.1
inHull = geometry::inhulln(datC2, as.matrix(toTest))
toUse = profileLogLik2[allPoints,][!inHull,]
toTest = profileLogLik2[allPoints,]
toUse <- toUse[order(toUse$x1),]
toUse <- head(toUse, - 1)
points(toTest[,1], toTest[,2]-chisqValue, col='red', cex=0.6)
points(toUse[,1], toUse[,2]-chisqValue, col='blue', cex=0.6, pch=3)

interp1 = mgcv::gam(profile ~ s(x1, k=nrow(toUse), m=1, fx=TRUE), data=toUse)
profaniso1 = data.frame(x1=seq(min(toUse$x1), max(toUse$x1), len=1001))
profaniso1$z = predict(interp1, profaniso1)
lines(profaniso1$x1, profaniso1$z-chisqValue, col = 'green')

abline(h =-chisqValue, lty = 2, col='black')
lower = min(profaniso1$x1)
upper = max(profaniso1$x1)
f1 <- approxfun(toUse[,1], toUse[,2])
MLE <- sqrt(paramsRenew[index[1],'anisoRatio']-1) * cos(2*(paramsRenew[index[1],'anisoAngleRadians']))
ci<-rootSolve::uniroot.all(f1, lower = lower, upper = upper)
abline(v =c(MLE,ci), lty = 2, col='black')


## aniso2
plot(profileLogLik$aniso2, profileLogLik$profile-chisqValue, cex=.2, xlab="aniso2", ylab="profileLogL", col = colAlpha$plot)
profileLogLik3 <- profileLogLik[,c('aniso2','profile')]
colnames(profileLogLik3) <- c("x1", 'profile')
datC2 = geometry::convhulln(profileLogLik3)
allPoints = unique(as.vector(datC2))
toTest = profileLogLik3[allPoints,]
toTest[,'profile'] = toTest[,'profile'] + 0.1
inHull = geometry::inhulln(datC2, as.matrix(toTest))
toUse = profileLogLik3[allPoints,][!inHull,]
toTest = profileLogLik3[allPoints,]
toUse <- toUse[order(toUse$x1),]
toUse <- head(toUse, - 1)
points(toTest[,1], toTest[,2]-chisqValue, col='red', cex=0.6)
points(toUse[,1], toUse[,2]-chisqValue, col='blue', cex=0.6, pch=3)

interp1 = mgcv::gam(profile ~ s(x1, k=nrow(toUse), m=1, fx=TRUE), data=toUse)
profaniso2 = data.frame(x1=seq(min(toUse$x1), max(toUse$x1), len=1001))
profaniso2$z = predict(interp1, profaniso2)
lines(profaniso2$x1, profaniso2$z-chisqValue, col = 'green')
abline(h =-chisqValue, lty = 2, col='black')
lower = min(profileLogLik3$x1)
upper = max(profileLogLik3$x1)

f1 <- approxfun(toUse[,1], toUse[,2])
MLE <- sqrt(paramsRenew[index[1],'anisoRatio']-1) * sin(2*(paramsRenew[index[1],'anisoAngleRadians']))
ci<-rootSolve::uniroot.all(f1, lower = lower, upper = upper)
abline(v =c(MLE,ci), lty = 2, col='black')


## boxcox
likForboxcox = cbind(boxcox, apply(LogLikcpu, 2,  max) )
f1 <- approxfun(likForboxcox[,1], likForboxcox[,2]-breaks)
plot(likForboxcox[,1], likForboxcox[,2]-breaks-chisqValue, ylab= "proLogL", xlab='Box-Cox', cex=0.5)
likForboxcox <- likForboxcox[order(likForboxcox[,1]),]
lines(likForboxcox[,1], likForboxcox[,2]-breaks-chisqValue, col='blue')
abline(h =-chisqValue, lty = 2)

lower = min(boxcox)
upper = max(boxcox)
ci<-rootSolve::uniroot.all(f1, lower = lower, upper = upper)
abline(v =c(boxcox[index[2]],ci), lty = 2)

```



## Step 2, get estimates for correlation parameters only
```{r 1, eval=FALSE}
result_2<-gpuLik::prof1dCov(LogLik = result_1$LogLik,  # cpu matrix
                   XVYXVX = result_1$XVYXVX,  # cpu matrix
                   ssqResidual = result_1$ssqResidual,  # cpu matrix
                   paramToEstimate = c('range','combinedRange','shape', 
                                       'nugget','aniso1', 'aniso2','boxcox'),
                   cilevel=0.9, 
                   params = result_1$paramsRenew, 
                   boxcox = result_1$boxcox,  
                   Ndata = result_1$Ndata,
                   Nobs = result_1$Nobs,
                   Ncov = result_1$Ncov,
                   reml = FALSE,
                   predictors = result_1$predictors,  # character string
                   verbose=FALSE)

# table of estimates
result_2$summary
# index for the MLE parameter set
result_2$mleIndex
```

## Step 3, get estimates and profile plots for betas'
```{r beta_profile, eval=TRUE, out.width="49%", cache=TRUE}
intercept<- sort(c(swissRes$summary['(Intercept)','estimate'], seq(0, 12, len=199)))
elevation  <- sort(c(swissRes$summary['elevation','estimate'], seq(-7, 15, len=199)*1e-04))
Betas <- cbind(intercept, elevation)

output<-gpuLik::Prof1dBetas(Betas=Betas,
                            cilevel=0.9,
                            Nobs = result_1$Nobs,
                            Ndata = result_1$Ndata,
                            Nparam = result_1$Nparam,
                            Ncov = result_1$Ncov,
                            detVar = result_1$detVar,
                            result_1$detReml,
                            result_1$ssqY,   
                            result_1$XVYXVX,   
                            result_1$jacobian,
                            convexHull = FALSE)

output$estimates
output$breaks
```



## Step 4, get stimates and profile plots for variance parameter
```{r sdSpatial, eval=TRUE, cache=TRUE, fig.show='hide'}
sdSpatial <- sort(c(seq(1.2, 5, len=39), swissRes$summary['sdSpatial','estimate']))
provarresult <- gpuLik::profVariance(sdSpatial, 
             cilevel=0.9,
             result_1$Nobs, 
             result_1$Ndata,
             result_1$Nparam,
             result_1$Ncov,
             result_1$detVar, 
             result_1$detReml, 
             result_1$ssqResidual, 
             result_1$jacobian)

provarresult$estimates
breaks <- provarresult$breaks

temp <- qchisq(cilevel,  df = 1)/2
LogLik <- provarresult$LogLik
```

```{r sdSpatial2, eval=TRUE, cache=TRUE}
plot(sdSpatial,LogLik-breaks-temp, cex=0.6, ylab='profileLogL')
lines(sdSpatial,LogLik-breaks-temp, col='blue')
abline(h=-temp, lty = 2)

abline(v=provarresult$estimates[c(1,2,3)], lty = 2)
text(provarresult$estimates[1], -3.7, round(provarresult$estimates[1],digits = 2))
text(provarresult$estimates[2], -3.7, round(provarresult$estimates[2],digits = 2))
text(provarresult$estimates[3], -3.7, round(provarresult$estimates[3],digits = 2))
```


## Show some 2-dimensional profile plots (setup)
```{r 2dplotsprep, cache=TRUE}
Spars = c("range",'sumLogRange',"combinedRange","nugget",'sdNugget',"shape",'aniso1','aniso2','anisoRatio','anisoAngleRadians',"alpha")
result = data.table::as.data.table(cbind(LogLikcpu, paramsRenew[,Spars]))
profileLogLik <- result[, .(profile=max(.SD)), by=Spars]
head(profileLogLik)


profileLogLik[,'profile'] <- profileLogLik[,'profile'] -maximum
profileLogLik <- profileLogLik[profile > -10]  
profileLogLik$logshape <- log(profileLogLik$shape)
profileLogLik <- as.data.frame(profileLogLik)

```


# 2-dimensional profile plot of sumLogRange vs nugget
```{r  sumLogRangenugget}
profileLogL <- profileLogLik[,c('sumLogRange','nugget','profile')]
datC2 = geometry::convhulln(profileLogL)
allPoints2 = unique(as.vector(datC2))
toTest2 = profileLogL[allPoints2,]
toTest2[,'profile'] = toTest2[,'profile'] - 0.1
inHull2 = geometry::inhulln(datC2, as.matrix(toTest2))
toUse2 = profileLogL[allPoints2,][inHull2,]
toTest2 = profileLogL[allPoints2,]

Sprob = c(0, 0.1, 0.2, 0.5, 0.8, 0.95, 0.99, 0.999, 1) 
Sbreaks =qchisq(Sprob, df=2)/2
Sbreaks = pmin(Sbreaks, 1000)
Sbreaks[1] = -10
SbreaksC = rev(- Sbreaks)
colDat2 = mapmisc::colourScale(profileLogL[,'profile'], style='fixed',
                               breaks=SbreaksC, 
                               col='Spectral', rev=TRUE)

interp2 = mgcv::gam(profile ~ s(sumLogRange, nugget, k=16, m=3,fx=TRUE), data=toUse2)
prof2list = list(sumLogRange=seq(15, 23, len=301),
                 nugget=seq(0, 0.6, len=301))
prof2 = do.call(expand.grid, prof2list)
prof2$z = predict(interp2, prof2)

col2 = mapmisc::colourScale(as.vector(prof2[,'z']), breaks=SbreaksC, col=colDat2$col, style='fixed')
colPoints = mapmisc::colourScale(toUse2[,'profile'], breaks=SbreaksC, col=col2$col, style='fixed')


plot(prof2[,c('sumLogRange','nugget')], col=col2$plot, pch=15)
points(toUse2[,c('sumLogRange','nugget')], col='black', cex=0.8)
mapmisc::legendBreaks('topright', breaks = rev(Sprob), col=colDat2$col)
```

## 2-dimensional profile plot of sumLogRange vs shape
```{r  rangevsshape}
profileLogL <- profileLogLik[ , c('sumLogRange','logshape', 'shape',  'profile')]

transFun = function(xx) xx^(-0.5)
invTransFun = function(xx) xx^(-2)

Sprob = c(0, 0.1, 0.2, 0.5, 0.8, 0.95, 0.99, 0.999, 1) 
Sbreaks =qchisq(Sprob, df=2)/2
Sbreaks = pmin(Sbreaks, 1000)
Sbreaks[1] = -10
SbreaksC = rev(-Sbreaks)
colDat2 = mapmisc::colourScale(profileLogL[,'profile'], style='fixed',
                               breaks=SbreaksC, 
                               col='Spectral', rev=TRUE)

Sshape = c(0.1, 1/4, 0.5, 1, 2, 5, 10, 100)

profForChull = cbind(
  sumLogRange = profileLogL$sumLogRange,
  shapeTrans = transFun(profileLogL$shape),
  profile=profileLogL$profile)


theHull = geometry::convhulln(profForChull)
toTest = profForChull[as.vector(theHull), ]
toTest[,'profile'] = toTest[,'profile'] - 0.1
inHull = geometry::inhulln(theHull, as.matrix(toTest))
toUse = toTest[inHull,]
toUse2 =  toUse[!duplicated(toUse[,c('sumLogRange','shapeTrans')]), ]


if(TRUE) {
  profForChullSub = profForChull[profileLogL$shape > 1 & profileLogL$shape < 8, ]
  theHullSub = geometry::convhulln(profForChullSub)
  toTestSub = profForChullSub[as.vector(theHullSub), ]
  toTestSub[,'profile'] = toTestSub[,'profile'] - 0.1
  inHullSub = geometry::inhulln(theHullSub, as.matrix(toTestSub))
  toUseSub = toTestSub[inHullSub,]
  toUse2 = rbind(toUse, toUseSub)
  toUse2 = toUse2[!duplicated(toUse2[,c('sumLogRange','shapeTrans')]), ]
}

theGridList = list(sumLogRange = seq(15, 23.3, len=201),
                   logshape = seq(-1.78, 4.6, len=201))
theGrid = do.call(expand.grid, theGridList)

theInterp = akima::interp(
  toUse2[,'sumLogRange'], toUse2[,'shapeTrans'], toUse2[,'profile'],
  theGridList$sumLogRange,
  transFun(exp(theGridList$logshape)),
  extrap=FALSE, linear=TRUE)


col2 = mapmisc::colourScale(as.vector(theInterp$z), breaks=SbreaksC, col=colDat2$col, style='fixed')
colPoints = mapmisc::colourScale(toUse2[,'profile'], breaks=SbreaksC, col=col2$col, style='fixed')

plot(theGrid[,'sumLogRange'],theGrid[,'logshape'], col=col2$plot, pch=15, ylab='logshape', xlab='sumLogRange')
points(toUse2[,'sumLogRange'], log(invTransFun(toUse2[, 'shapeTrans'])), cex=0.8)
```













